### 2016-07-14 version0.0/intro0.0.tex
Update intro0.0.tex
edits to ISM section

\section{Components of the Interstellar Medium} 
\label{sec: ism_intro}
%how do we observe it
%what the observation tell us
% how do we measure the dust and gas
The interstellar medium in galaxies is a complex system with a wide range of structures, but these structures can be divided into two main components: gas and dust.
The gas in the ISM of galaxies is mostly made of hydrogen and helium with 1 per cent heavier elements (metals), and can be in the form of clouds or diffuse regions.
Gas clouds include molecular clouds, cold neutral atomic hydrogen (\hi) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or hot intercloud medium.
Dust mostly contains silicate, graphite grains can be seen in dark clouds or galactic cirrus.
Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds and 21~cm emission of \hi~are the main observational signatures of the gas in the ISM of galaxies.
Dust can be observed directly through far-infrared and sub-millimeter wavelength emission or indirectly through its extinction and attenuation effects (see Sec.~\ref{sec: extinction}).

Molecular clouds in the ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$); masses of molecular clouds range from a few to millions of solar masses~\citep{Bolato08}.
Density in the molecular clouds is not uniform; There are dense and colds clumps inside these clouds.
Since these clumps are ideal places to form stars, studying molecular clouds has an important role in understanding formation of stars
However, H$_2$ molecules, the main component of molecular clouds, have no permanent electric dipole moment which makes them difficult to detect.
The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but these clouds also contain heavier elements such as carbon monoxide, hydrogen cyanide, water, ammonia and more than tens of others.
Carbon monoxide (CO) molecules are the third-most abundant constituent of molecular clouds.
In fact, most of our knowledge from molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low rotational state} and can be excited in the temperature of molecular clouds. %PB \bf needs clarification
Other heavier molecules have emission lines which are also detectable in the spectrum of clouds (specially galactic ones), but observing CO emission is the most common way to study the properties of molecular clouds i.e. their mass (see Sec.~\ref{sec: ismmap} for more details).

The molecular clouds are surrounded by clouds of atomic gas~\citep{Kennicutt12}, which are easily traceable by 21-cm emission.
Hydrogen atoms in the ISM (excluding the regions close to hot stars, see below) are in their ground state. 
The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. the proton's spin is up and the electron's spin is down or vice versa). 
The energy state of the anti-parallel mode is slightly less than the parallel mode.
Since atoms always want to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
However, the difference between these two states is very small and it takes millions of years before the transition happens.
The large amount of hydrogen atoms compensates for the rareness of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
Observation of the \hi atoms is specifically necessary for understanding physical properties and dynamics of the ISM, which leads to understanding the star formation process~\citep{Walter08}.

\hii~regions are hot and low density regions that are mostly located in the disks of spiral galaxies.
High energy UV photons emitted by massive new born stars have sufficient energy to ionize their surrounding gas, and
~\halpha emission is the main observational feature of \hii~regions.
The temperature and density of these regions can be estimated by observing other recombination lines such as H$\beta$, and forbidden lines such as \sii, \oii, \oiii, and \nii. 
Forbidden lines are not ``forbidden", they only have much lower probability of occurring than the ``allowed" ones.
Optically bright \halpha emission from \hii~regions correlates with number of new massive stars in regions and can be used as a star formation tracer~\citep[e.g.][]{Kennicutt98b,Calzetti13}.
Studying \hii~regions provides valuable insight into star forming regions by providing information such as star formation rate, initial mass function (IMF), and distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.

Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
%The total gas mass of galaxies can be determined using optical depth in sub-mm waveband of dust emission. 
In spiral galaxies dust grains are located in cold regions ($\sim$30~K) and have a power-law distribution of size.
Source of dust thermal emission is from stars and shape of the continuum depends on size of the grain.
Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate mass young stars~\cite{Peeters04}. 
Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
Dust is the main source of extinction and reddening of starlight (See Sec.\ref{sec: extinction} for more information).

\subsection{Mapping the Interstellar Medium} 
\label{sec: ismmap}
Measuring the mass of gas in galaxies is a necessary step to know how much raw material is available for forming stars.
A map of the total gas mass in the ISM can be produced by direct observations of gas or using interstellar dust as a tracer. 
Neutral atomic and molecular hydrogen are the most common components of the ISM. 
Therefore, to produce a total gas mass map in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly helium, which cannot be observed directly. 
Another way to do the mapping is to assume that the ratio of total gas to dust is constant across the galaxy, and convert dust observations to a map of total gas mass.

@@

The surface density of gas in the ISM of galaxies can be measured by direct observation of the neutral and molecular hydrogen.
This method can be promising if observational data with resolved molecular and atomic clouds are available.
However, given the state of the current technology, having the high resolution images of clouds for most of galaxies are not possible. 
This problem shows itself for distant galaxies more than nearby galaxies. 
As a result, using images of molecular and atomic cloud to measure surface density of gas in ISM is limited to telescopes resolution.

@@

\cite{Young91} described the relationship between the CO luminosity of a cloud and its mass. The CO luminosity of a cloud is:
\begin{equation}
L_{CO} = D^2 \int I_{\rm CO} d\Omega 
\end{equation}
where $D$ is the distance to the cloud and 
$I_{\mathrm CO}$ is the CO brightness temperature integrated over the line profile in KKms$^{-1}$.
It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(k) is the peak brightness temperature in the CO line and $V$ is the line-width in Kms$^{-1}$.
For a uniform cloud with a radius $R$, the CO luminosity is given by:
 \begin{equation}
L_{\rm CO} = \pi R^2 T_{\rm CO} \Delta V
\end{equation}

Giant molecular clouds are self-gravitating systems~\citep[e.g.][]{Efstathiou83,Blitz99}.
Thus, using the virial theorem leads to calculating the mass of the cloud: 
 \begin{equation}
 \label{equ: vir}
 M_{cloud} = L_{\rm CO} \sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}}
 \end{equation}
 where $\rho$ is the mass density of the cloud and $\sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}}$ is called the conversion factor.
 Equ.~\ref{equ: vir} shows that the total mass of molecular clouds and the CO luminosity of the cloud are directly related~\citep{Young91}. 
 Since the dependency of $I_{\mathrm CO}$ to optical depth is negligible~\citep{Krumholz09}, total CO luminosity of the galaxies, can be used to measure the total H$_2$ mass of galaxies.
 The relation between CO emission and H$_2$ cloud mass is shown as
\begin{equation}
N_{\rm H_2}/\rm cm^{-2} = X_{\rm CO} \times I_{\rm CO}/{\rm K km s}^{-1}
\end{equation}
where X$_{\rm CO}$ is the conversion factor (also known as the X-factor).
The X-factor is different in each galaxy and sometimes is even different in regions within a galaxy due to differences in properties such as metallicity. 
Though assuming a constant conversion factor for galaxies like M82 and M31 can lead to accurate estimation of global molecular gas mass, in regions with low metallicity there are uncertainties~\citep{Bolato13}. 
Various groups are working on observations of different types of galaxies to measure the X-factor for them~\citep{Wilson95, Bosselli02, Bolato13}.

@@

In order to empirically determine the relation between H$_2$ masses and CO luminosities, many observational attempts have been made on both Galactic and extragalactic scales. 
One of the most significant studies in this regard was done by~\cite{Solomon87}, who studied this relation over more than 273 clouds inside the Milky Way and found a strong correlation between the virial mass of molecular clouds and CO luminosity. 
In Local Group galaxies, several groups have measured size, line width, and CO luminosity of molecular clouds and investigated the relation between  their virial masses and CO emission in environment other than the Milky Way. 
Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32~\citep[e.g.,][]{Wilson89, Wilson90}. 
Fig.~\ref{fig: mco_ch} shows the CO luminosity verses virial masses of molecular clouds in the Milky Way, M31, M33, and IC~10. 
The extragalactic molecular clouds are similar to those in the Milky Way. 
The conversion between the CO luminosity and H$_2$ masses is still a controversial topic~\citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}.
Problems regarding metallicity are not yet solved and it is still not clear whether the conversion factor is global or local. 
Extragalactic investigations were limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes. 
To measure the clouds in distant galaxies, spatial resolution of maps must be better than 40 pc which is the typical size of a giant molecular cloud~\citep[e.g.][and refrences therein]{Young91,Bolato13}.

Atomic gas in galaxies are dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
Assuming optically thin lines for \hi~emission, the intensity of the 21-cm emission is proportional to the density of the atomic hydrogen, $N_{H {\sc I}}$~(cm$^{-3}$), along the line-of-sight.
\begin{equation}
N_{H {\sc I}}  \propto \int T_{\mathrm B} dV
\end{equation}
where $T_{\mathrm B}$ is the temperature brightness in K and dV is in Kms$^{-1}$, with the integral over the line profile. 
These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick~\citep{Braun09}.

@@

Studying the gas clouds in the ISM of distant galaxies by using direct methods is almost impossible and not practical, due to low spatial resolution of data.
\cite{Hildebran83} was the first to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin. 
The Herschel Space Telescope \cite{Pilbratt10} measured the continuum dust emission from hundreds of galaxies\citep{Eales10, Oliver12}. 
This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission. 
The observed FIR flux has almost no dependency on distance, thus, one of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, high spatial resolution is not necessary. 
The other important advantage is that this method solves the newly-found problem of the ``dark gas" in galaxies. 
Dark gas is a significant fraction of gas in galaxies which is traced by neither 21-cm emission nor CO emission~\citep{Abdo10}. 
As such it is very difficult to detect with telescopes, but an accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.

There are disadvantages of the use of the gas to dust ratio to trace gas in the ISM.
In order to use the dust as a tracer of the gas mass, first a relationship between the optical depth and the mass of the dust and then a relationship between the mass of the dust and the mass of the gas must be derived.
\cite{Draine03} pointed out that the former approach is uncertain because of the uncertainly in the radiative efficiency of dust grains. 
Measuring the gas to dust ratio in galaxies are not accurate, neither~\citep{Hildebran83}, which means that there are problems in both steps. 
In addition, the dust method has two major practical problems: firstly, to apply this method, knowing the temperature of the dust is necessary. 
To solve this problem, measurement of the continuum emission at far-infrared wavelengths long enough to cover the peak of the emission must be very accurate~\citep{Ealas12}. 
The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas~\citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved. 
This method is the best alternative for measuring the total gas in galaxies, that there is no observation of CO or \hi~emission.

\subsection{The ISM and starlight: extinction and attenuation}
\label{sec: extinction}
Dust in ISM affects stellar emission by attenuating, scattering or absorption.
Attenuation refers to the effects of dust with embedded light sources distributed throughout. 
The dust itself can be clumpy or smooth. 
Effect of dust clouds with embedded light sources on distribution of the light is called attenuation.
The dust cloud could have any distribution and be clumpy or smooth.
Since both light source and dust have extended distribution, the relative location of the dust and light source affect the net absorbed and scattered light.
The other parameters that is important on  the scattering and absorption is the relative position of dust and observer.
When the dust is in the line of sight, attenuation will make the emerging light dimmer~\citep[e.g.][and references therein]{Calzetti13}.
This is the typical situation that occurs when studying galaxies or extended regions within galaxies.

Extinction happens when there is a combination of both absorption and scattering of radiation by dust and varies with the wavelength of emission; UV light passes through dust are more affected than the optical light.
Extinction can be defined as reduction of the original intensity caused by dust:
\begin{equation}
\label{equ: extinction}
{\mathrm I}(\lambda) = {\mathrm I}_0(\lambda)exp[-\tau_{\lambda}]
\end{equation}
where I$(\lambda)$ is observed intensity in wavelength $\lambda$, I$_0(\lambda)$ is intensity of light before passing through dust, and $\tau_{\lambda}$ is extinction in $\lambda$.
The extinction depends also on size of grains and extinction cross section.
For measuring SFR using varies wavebands, 
decreasing of the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR. 
% By converting Equ.~\ref{equ: extinction} to magnetidue system:
% \begin{equation}
%      {\mathrm m}_{\lambda} - {\mathrm m_0}_{\lambda}  = -2.5\log(\frac{{\mathrm I}(\lambda)}{{\mathrm I}_0(\lambda)})
% \end{equation}
% and by substituting $\frac{{\mathrm I}(\lambda)}{{\mathrm I}_0(\lambda)}$ with $exp[-\tau_{\lambda}]$, we have:
% \begin{equation}
% \begin{split}
%     {\mathrm m}_{\lambda} - {\mathrm m_0}_{\lambda} & = -2.5\log(exp[-\tau_{\lambda}]) \\
%               & = 1.086\tau_{\lambda}
% \end{split}
% \end{equation}
% By defining ${\mathrm m}_{\lambda} - {\mathrm m_0}_{\lambda} & = {\mathrm A}_{\lambda}$  extinction in magnitude is A$_{\lambda} = 1.086\tau_{\lambda}$.

>>>>

\section{Components of the Interstellar Medium} 
\label{sec: ism_intro}
%how do we observe it
%what the observation tell us
% how do we measure the dust and gas
The interstellar medium in galaxies is a complex system with a wide range of structures, but these structures can be divided into two main components: gas and dust.
The gas in the ISM of galaxies is mostly made of hydrogen and helium with 1 per cent heavier elements (metals), and can be in the form of clouds or diffuse regions.
Gas clouds include molecular clouds, cold neutral atomic hydrogen (\hi) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or a hot intercloud medium.
Dust mostly contains silicate and graphite grains, and can be seen in dark clouds or galactic cirrus. %PB: please check changes to this sentence
Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds and 21~cm emission of \hi~are the main observational signatures of the gas in the ISM of galaxies.
Dust can be observed directly through far-infrared and sub-millimeter wavelength emission or indirectly through its extinction and attenuation effects (see Sec.~\ref{sec: extinction}).

Molecular clouds in the ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$); masses of molecular clouds range from a few to millions of solar masses~\citep{Bolato08}.
Density in the molecular clouds is not uniform; there are dense and colds clumps inside these clouds.
Since these clumps are ideal places to form stars, studying molecular clouds has an important role in understanding formation of stars.
However, H$_2$ molecules, the main component of molecular clouds, have no permanent electric dipole moment which makes them difficult to detect.
The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but these clouds also contain heavier elements such as carbon monoxide, hydrogen cyanide, water, ammonia and more than tens of others.
Carbon monoxide (CO) molecules are the third-most abundant constituent of molecular clouds.
In fact, most of our knowledge from molecular clouds comes from observing the line emission of CO molecules, which {\bf due to their heavy weight, they have very low rotational state} and can be excited in the temperature of molecular clouds. %PB \bf needs clarification
Other heavier molecules have emission lines which are also detectable in the spectra of clouds (especially Galactic ones), but observing CO emission is the most common way to study the properties of molecular clouds e.g.\ their mass (see Sec.~\ref{sec: ismmap} for more details).

The molecular clouds are surrounded by clouds of atomic gas~\citep{Kennicutt12}, which are easily traceable by 21-cm emission.
Hydrogen atoms in the ISM (excluding the regions close to hot stars, see below) are in their ground state. 
The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. the proton's spin is up and the electron's spin is down or vice versa). 
The energy state of the anti-parallel mode is slightly less than the parallel mode.
Since atoms always want to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
However, the energy difference between these two states is very small and it takes millions of years before the transition happens.
The large amount of hydrogen atoms compensates for the rarity of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
Observation of the \hi atoms is specifically necessary for understanding physical properties and dynamics of the ISM, which leads to understanding the star formation process~\citep{Walter08}.

\hii~regions are hot and low density regions that are mostly located in the disks of spiral galaxies.
High energy UV photons emitted by massive newborn stars have sufficient energy to ionize their surrounding gas, and
~\halpha emission is the main observational feature of \hii~regions.
The temperature and density of these regions can be estimated by observing other recombination lines such as H$\beta$, and forbidden lines such as \sii, \oii, \oiii, and \nii. 
Forbidden lines are not strictly ``forbidden"; they only have much lower probability of occurring than the ``allowed" ones.
Optically bright \halpha emission from \hii~regions correlates with the number of new massive stars in regions and can be used as a star formation tracer~\citep[e.g.][]{Kennicutt98b,Calzetti13}.
Studying \hii~regions provides valuable insight into star forming regions by providing information such as the star formation rate, the initial mass function (IMF) of stars, and the distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.

Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
%The total gas mass of galaxies can be determined using optical depth in sub-mm waveband of dust emission. 
In spiral galaxies dust grains are located in cold regions ($\sim$30~K) and have a power-law distribution of size.
The source of dust thermal emission is heating from stars and the shape of the continuum depends on size of the grain.
Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate mass young stars~\cite{Peeters04}. 
Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in the far-infrared~\citep[e.g.][]{Calapa14, lu14}
Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).

\subsection{Mapping the Interstellar Medium} 
\label{sec: ismmap}
Measuring the mass of gas in galaxies is a necessary step to know how much raw material is available for forming stars.
A map of the total gas mass in the ISM can be produced by direct observations of gas or using interstellar dust as a tracer. 
Neutral atomic and molecular hydrogen are the most common components of the ISM. 
Therefore, to produce a total gas mass map in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements (mostly helium), which cannot be observed directly. 
Another way to do the mapping is to assume that the ratio of total gas to dust is constant across the galaxy, and convert dust observations to a map of total gas mass.

@@

The surface density of gas in the ISM of galaxies can be measured by direct observation of the neutral and molecular hydrogen.
This method can be promising if observational data with resolved molecular and atomic clouds are available.
However, given the state of current technology, having high resolution images of clouds for most galaxies is not possible. 
This problem shows itself for distant galaxies more than nearby galaxies. 
As a result, using images of molecular and atomic clouds to measure surface density of gas in ISM is limited by telescopes' resolution.

@@

\cite{Young91} described the relationship between the CO luminosity of a cloud and its mass. The CO luminosity of a cloud is:
\begin{equation}
L_{CO} = D^2 \int I_{\rm CO} d\Omega 
\end{equation}
where $D$ is the distance to the cloud and 
$I_{\mathrm CO}$ is the CO brightness temperature integrated over the line profile in K~km~s$^{-1}$.
It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(K) is the peak brightness temperature in the CO line and $V$ is the line-width in km~s$^{-1}$.
For a uniform cloud with a radius $R$, the CO luminosity is given by:
 \begin{equation}
L_{\rm CO} = \pi R^2 T_{\rm CO} \Delta V
\end{equation}

Giant molecular clouds are self-gravitating systems~\citep[e.g.][]{Efstathiou83,Blitz99}.
Thus, using the virial theorem leads to calculating the mass of the cloud: 
 \begin{equation}
 \label{equ: vir}
 M_{cloud} = L_{\rm CO} \sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}}
 \end{equation}
 where $\rho$ is the mass density of the cloud and $\sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}}$ is called the conversion factor.
 Equ.~\ref{equ: vir} shows that the total mass of molecular clouds and the CO luminosity of the cloud are directly related~\citep{Young91}. 
 Since the dependency of $I_{\mathrm CO}$ on optical depth is negligible~\citep{Krumholz09}, the total CO luminosity of a galaxy can be used to measure its total H$_2$ mass.
 The relation between CO emission and H$_2$ cloud mass is shown as:
\begin{equation}
N_{\rm H_2}/\rm cm^{-2} = X_{\rm CO} \times I_{\rm CO}/{\rm K km s}^{-1}
\end{equation}
where X$_{\rm CO}$ is the conversion factor (also known as the X-factor).
The X-factor is different in each galaxy and sometimes is even different in regions within a galaxy due to differences in properties such as metallicity. 
Though assuming a constant conversion factor for galaxies like M82 and M31 can lead to accurate estimation of global molecular gas mass, in regions with low metallicity there are uncertainties~\citep{Bolato13}. 
Various groups are working on observations of different types of galaxies to measure the X-factor for them~\citep{Wilson95, Bosselli02, Bolato13}.

@@

In order to empirically determine the relation between H$_2$ masses and CO luminosities, many observational attempts have been made on both Galactic and extragalactic scales. 
One of the most significant studies in this regard was done by~\cite{Solomon87}, who studied this relation over more than 273 clouds inside the Milky Way and found a strong correlation between the virial mass of molecular clouds and CO luminosity. 
In Local Group galaxies, several groups have measured size, line width, and CO luminosity of molecular clouds and investigated the relation between  their virial masses and CO emission in environments other than the Milky Way. 
Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32~\citep[e.g.,][]{Wilson89, Wilson90}. 
Fig.~\ref{fig: mco_ch} shows the CO luminosity verses virial masses of molecular clouds in the Milky Way, M31, M33, and IC~10. 
The extragalactic molecular clouds are similar to those in the Milky Way. 
The conversion between the CO luminosity and H$_2$ masses is still a controversial topic~\citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}.
Problems regarding metallicity are not yet solved and it is still not clear whether the conversion factor is global or local. 
Extragalactic investigations have been limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes. 
To measure the clouds in distant galaxies, the spatial resolution of maps must be better than 40 pc, which is the typical size of a giant molecular cloud~\citep[e.g.][and refrences therein]{Young91,Bolato13}.

Atomic gas in galaxies is dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
Assuming optically thin lines for \hi~emission, the intensity of the 21-cm emission is proportional to the density of the atomic hydrogen, $N_{H {\sc I}}$~(cm$^{-3}$), along the line-of-sight.
\begin{equation}
N_{H {\sc I}}  \propto \int T_{\mathrm B} dV
\end{equation}
where $T_{\mathrm B}$ is the temperature brightness in K and dV is in km~s$^{-1}$, with the integral over the line profile. 
These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick~\citep{Braun09}.

@@

Studying the gas clouds in the ISM of distant galaxies by using direct methods is almost impossible and not practical, due to low spatial resolution of data.
\cite{Hildebran83} was the first to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin. 
The Herschel Space Telescope \cite{Pilbratt10} measured the continuum dust emission from hundreds of galaxies\citep{Eales10, Oliver12}. 
This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission. 
The observed FIR flux has almost no dependence on distance, thus, one of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, high spatial resolution is not necessary. 
The other important advantage is that this method solves the newly-found problem of the ``dark gas" in galaxies. 
Dark gas is a significant fraction of gas in galaxies which is traced by neither 21-cm emission nor CO emission~\citep{Abdo10}. 
As such it is very difficult to detect with telescopes, but an accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.

There are disadvantages of the use of the gas to dust ratio to trace gas in the ISM.
In order to use the dust as a tracer of the gas mass, first a relationship between the optical depth and the mass of the dust and then a relationship between the mass of the dust and the mass of the gas must be derived.
\cite{Draine03} pointed out that the former approach is uncertain because of the uncertainly in the radiative efficiency of dust grains. 
Measuring the gas to dust ratio in galaxies are not accurate, neither~\citep{Hildebran83}, which means that there are problems in both steps. 
In addition, the dust method has two major practical problems: firstly, to apply this method, knowing the temperature of the dust is necessary. 
To solve this problem, measurement of the continuum emission at far-infrared wavelengths long enough to cover the peak of the emission must be very accurate~\citep{Ealas12}. 
The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas~\citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved. 
This method is the best alternative for measuring the total gas in galaxies where there are no observations of CO or \hi~emission.

\subsection{The ISM and starlight: extinction and attenuation}
\label{sec: extinction}
Dust in ISM affects stellar emission by attenuating, scattering or absorption.
Attenuation refers to the effects of dust with embedded light sources distributed throughout. 
The dust itself can be clumpy or smooth. 
The effect of dust clouds with embedded light sources on the distribution of the light is called attenuation.
The dust cloud could have any distribution and be clumpy or smooth.
Since both light sources and dust have an extended distribution, the relative locations of the dust and light sources affect the net absorbed and scattered light.
The other parameter that is important for the scattering and absorption is the relative position of dust and observer.
When the dust is in the line of sight, attenuation will make the emerging light dimmer~\citep[e.g.][and references therein]{Calzetti13}.
This is the typical situation that occurs when studying galaxies or extended regions within galaxies.

Extinction happens when there is a combination of both absorption and scattering of radiation by dust and varies with the wavelength of emission; UV light passing through dust is more affected than visible light.
Extinction can be defined as a reduction of the original intensity caused by dust:
\begin{equation}
\label{equ: extinction}
{\mathrm I}(\lambda) = {\mathrm I}_0(\lambda)exp[-\tau_{\lambda}]
\end{equation}
where I$(\lambda)$ is the observed intensity in wavelength $\lambda$, I$_0(\lambda)$ is the intensity of light before passing through dust, and $\tau_{\lambda}$ is the otpical depth at wavelength $\lambda$.
The extinction depends also on the size of grains and their extinction cross section.
For measuring SFR using various wavebands, 
the decrease in the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR. 
% By converting Equ.~\ref{equ: extinction} to magnetidue system:
% \begin{equation}
%      {\mathrm m}_{\lambda} - {\mathrm m_0}_{\lambda}  = -2.5\log(\frac{{\mathrm I}(\lambda)}{{\mathrm I}_0(\lambda)})
% \end{equation}
% and by substituting $\frac{{\mathrm I}(\lambda)}{{\mathrm I}_0(\lambda)}$ with $exp[-\tau_{\lambda}]$, we have:
% \begin{equation}
% \begin{split}
%     {\mathrm m}_{\lambda} - {\mathrm m_0}_{\lambda} & = -2.5\log(exp[-\tau_{\lambda}]) \\
%               & = 1.086\tau_{\lambda}
% \end{split}
% \end{equation}
% By defining ${\mathrm m}_{\lambda} - {\mathrm m_0}_{\lambda} & = {\mathrm A}_{\lambda}$  extinction in magnitude is A$_{\lambda} = 1.086\tau_{\lambda}$.
